Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip0.tex
Add action item on Pi_int binding proof

	Protocol:
	\begin{enumerate}
		\item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
		\item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$,
			where on $\PiMeasure$'s fourth message, the prover can instead choose to abort by sending $a=\bot$.
			This is useless for the cheating prover but useful for proving one of our theorems later. \Ethan{Where/how to say this?}
			If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
			If it's a Hadamard round, the verifier obtains $v$.
		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$

@@

\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of $\PiNaive$]
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	then the verifier's output in the Hadamard round is $(\varepsilon+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}

\begin{proof}
	By \Cref{lem:urmila-binding},
	there exist some $\rho$ such that
	$v\approx_{c,\negl(\lambda)}M_{XZ}(\rho,h)$.
	Let $\cVVer$ be the verification operation in \stepref{qpip1-verify} of $\PiSamp$.
	Since $\cVVer$ is efficient, we have
	$(d,z)\approx_{c, \negl(\lambda)}\cVVer(M_{XZ}(\rho, h))$.
	\Ethan{There were some shenanigans involving subnormalized states for which I'm not quite sure what's going on.}
	By \Cref{QPIP1thm}, for all $\rho$, 
	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \varepsilon}(d, z_{ideal})$.
	So we conclude that
	$(d, z)\approx_{c, \varepsilon+\negl(\lambda)}(d, z_{ideal})$.
\end{proof}

>>>>

	Protocol:
	\begin{enumerate}
		\item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
		\item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$,
			where on $\PiMeasure$'s second message, the prover can instead choose to abort by sending $a=\bot$.
			This is useless for the cheating prover but useful for proving one of our theorems later. \Ethan{Where/how to say this?}
			If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
			If it's a Hadamard round, the verifier obtains $v$.
		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$

@@

\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of $\PiNaive$]
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	\Ethan{Wrong assumption. The ``perfect prover" notion here is generalized and allows giving up.}
	then the verifier's output in the Hadamard round is $(\varepsilon+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}

\begin{proof}
	\Ethan{TODO this is currently wrong and I'm not sure how to fix it.
	The version before this which had subnormalized states seems strange too.
	The correct proof should involve an alternative prover strategy that ``fixes" the abort case
	by re-running with perfect prover strategy,
	in order to connect the dots with \Cref{lem:urmila-binding}}
	By \Cref{lem:urmila-binding},
	there exist some $\rho$ such that
	$v\approx_{c,\negl(\lambda)}M_{XZ}(\rho,h)$.
	Let $\cVVer$ be the verification operation in \stepref{qpip1-verify} of $\PiSamp$.
	Since $\cVVer$ is efficient, we have
	$(d,z)\approx_{c, \negl(\lambda)}\cVVer(M_{XZ}(\rho, h))$.
	\Ethan{There were some shenanigans involving subnormalized states for which I'm not quite sure what's going on.}
	By \Cref{QPIP1thm}, for all $\rho$, 
	$\cVVer(M_{XZ}(\rho, h))\approx_{c, \varepsilon}(d, z_{ideal})$.
	So we conclude that
	$(d, z)\approx_{c, \varepsilon+\negl(\lambda)}(d, z_{ideal})$.
\end{proof}
